---
title: "Assignment 3"
author: "Jacob Fabian"
date: "2022-10-09"
output:
  pdf_document: default
  html_document: default
---

```{r}
library("dplyr")
library("tidyr")
library("ggplot2")
library("rpart")
library("caret")
library('FNN')
library('melt')
library('MASS') 
library('reshape2') 
setwd("~/Downloads")
```

```{r}
bank = read.csv("UniversalBank.csv")
bank$Personal.Loan = as.factor(bank$Personal.Loan)
bank$Online = as.factor(bank$Online)
bank$CreditCard = as.factor(bank$CreditCard)
set.seed(1)
train.index <- sample(row.names(bank), 0.6*dim(bank)[1])  
test.index <- setdiff(row.names(bank), train.index) 
train.df <- bank[train.index, ]
test.df <- bank[test.index, ]
train <- bank[train.index, ]
test = bank[train.index,]
```
###A. Create a pivot table for the training data with Online as a column variable, CC as a row variable, and Loan as a secondary row variable. The values inside the table should convey the count. In R use functions melt() and cast(), or function table(). In Python, use panda dataframe methods melt() and pivot(). 

```{r}
melted.bank = melt(train.df,id=c("CreditCard","Personal.Loan"),variable= "Online")
recast.bank=dcast(melted.bank,CreditCard+Personal.Loan~Online)
recast.bank[,c(1:2,14)]
```
###Consider the task of classifying a customer who owns a bank credit card and is actively using online banking services. Looking at the pivot table, what is the probability that this customer will accept the loan offer? [This is the probability of loan acceptance (Loan = 1) conditional on having a bank credit card (CC = 1) and being an active user of online banking services (Online = 1)]. 

###2.6%

```{r}
melted.bankc1 = melt(train,id=c("Personal.Loan"),variable = "Online")
melted.bankc2 = melt(train,id=c("CreditCard"),variable = "Online")
recast.bankc1=dcast(melted.bankc1,Personal.Loan~Online)
recast.bankc2=dcast(melted.bankc2,CreditCard~Online)
Loanline=recast.bankc1[,c(1,13)]
LoanCC = recast.bankc2[,c(1,14)]

Loanline
```

```{r}
LoanCC
```
###d. Compute the following quantities [P (A | B) means “the probability of A given B”]:P (CC = 1 | Loan = 1) (the proportion of credit card holders among the loan acceptors)P(Online=1|Loan=1)P (Loan = 1) (the proportion of loan acceptors)P(CC=1|Loan=0)P(Online=1|Loan=0)P(Loan=0)

```{r}
table(train[,c(14,10)])
```

```{r}
table(train[,c(13,10)])
```

```{r}
table(train[,c(10)])
```

### I.28%
### II. 60.3%
### III. .2%
### IV. 29.4%
### V. 58.3%
### VI. 90.8%

###Use the quantities computed above to compute the naive Ba1 probability P(Loan = 1 | CC = 1, Online = 1).

```{r}
((77/(77+198))*(166/(166+109))*(275/(275+2725)))/(((77/(77+198))*(166/(166+109))*(275/(275+2725)))+((801/(801+1924))*(1588/(1588+1137))*2725/(2725+275)))
```
### f. Compare this value with the one obtained from the pivot table in (b). Which is a more accurate estimate? 9.05% are very similar to the 9.7% the difference between the exact method and the naive-baise method is the exact method would need the the exact same independent variable classifications to predict, where the naive bayes method does not.

### g. Which of the entries in this table are needed for computing P (Loan = 1 | CC = 1, Online = 1)? In R, run naive Bayes on the data. Examine the model output on training data, and find the entry that corresponds to P (Loan = 1 | CC = 1, Online = 1). Compare this to the number you obtained in (e).


```{r}
naive.train = train.df[,c(10,13:14)]
naive.test = test.df[,c(10,13:14)]
naivebayes = naiveBayes(Personal.Loan~.,data=naive.train)
naivebayes
```

###(.280)(.603)(.09)/(.280.603.09+.29.58.908) = .09 which is the same response provided in the previous methods.
