---
title: "Assignment 4"
author: "Jacob Fabian"
date: "2022-10-29"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(readr)
library(cluster)
```



```{r}
Pharmaceuticals_1_ <- read_csv("Pharmaceuticals (1).csv")
View(Pharmaceuticals_1_)
head(Pharmaceuticals_1_)
```



```{r}
p1 <- Pharmaceuticals_1_[,3:11]
head(p1)
```


```{r}
ps <- scale(p1)
head(ps)
```

```{r}
wss <- (nrow(Pharmaceuticals_1_)-1)*sum(apply(ps,2,var))
wss
```

```{r}
library(stats)
for (i in 2:15) wss[i] <- sum(kmeans(ps,centers=i)$withinss)
wss
```

```{r}
plot(1:15, wss, type="b", xlab="Number of Clusters",ylab="Within groups sum of squares")
```

```{r}
fit <- kmeans(ps, 5)
aggregate(ps, by=list (fit$cluster), FUN=mean)
```

```{r}
ps1 <- data.frame(ps, fit$cluster)
ps1
```

```{r}
clusplot(ps,fit$cluster, color=TRUE, shade=TRUE, labels=2, lines=0)
```

###Cluster 1 - Row 11,17

###Cluster 2 - Row 2,6,18

###Cluster 3 - Row 1,3,7,9,16,21

###Cluster 4 - Row 5,8,9,12,14,20

###Cluster 5 - Row 4,13,15

###Due to the aggregate(ps,by=list(fit$cluster),FUN=mean)

###Cluster 1 has highest Net Profit Margin, lowest Beta, PE Ratio, and Rev growth.

###Cluster 2 has highest Beta, Leverage, Rev growth and the lowest Market Cap

###Cluster 3 has lowest Leverage.

###Cluster 4 has highest PE ratio, lowest ROE, ROA, Asset Turnover, and Net Profit Margin

###Cluster 5 has highest Market Cap, ROE, ROA, and Asset Turnover


###There is pattern in the clusters. Cluster 4 with highest PE ratio, lowest ROE, ROA, Asset Turnover, Net Profit Margin has a Hold recommendation.Cluster 5 with highest Market Cap, ROE, ROA, and Asset Turnover has a buy recommendation. 

###We can name various clusters 
###Cluster 1 - High Net Profit Margin, Low Beta, PE Ratio, Rev growth cluster

###Cluster 2 - High Beta, Leverage, Rev growth and Low Market Cap cluster

###Cluster 3 - Lowest Leverage cluster

###Cluster 4 - High PE ratio, Low ROE, ROA, Asset Turnover, Net Profit Margin Cluster

###Cluster 5 - High Market Cap, ROE, ROA, Asset Turnover cluster

