---
title: "Untitled"
author: "Jacob Fabian"
date: "2022-11-25"
output:
  pdf_document: default
  html_document: default
---


```{r}
library(readr)
library(cluster) 
library(dplyr)
setwd("~/Downloads")
```

```{r}
Cereals <- read_csv("Cereals.csv")
View(Cereals)
```

```{r}
head(Cereals) 
Cereals <- na.omit(Cereals)
head(Cereals)
```

```{r}
Cereals.norm <- Cereals %>%
    as_tibble() %>%
    mutate(across(where(is.numeric), scale))
```

```{r}
distance <- dist(Cereals.norm[4:16], method = "euclidean")
hc_single <- agnes(Cereals.norm[4:16], method = "single")
hc_complete <- agnes(Cereals.norm[4:16], method = "complete")
hc_average <- agnes(Cereals.norm[4:16], method = "average")
hc_ward <- agnes(Cereals.norm[4:16], method = "ward")
```

```{r}
print(hc_single)
print(hc_complete)
print(hc_average)
print(hc_ward)
```
###The highest coefficient will be the best method

### Single - 0.607
### Compete - 0.835
### Average - 0.777
### Ward - 0.904

### Since Ward has the highest coefficient we will look at that

```{r}
pltree(hc_ward, cex = 0.6, hang = -1, main = "Dendrogram of agnes")
```


```{r}
plot(hc_ward)
rect.hclust(hc_ward, k = 6, border = 1:6)
```

### 6 Clusters would be the best

```{r}
model <- kmeans(Cereals.norm[4:16], centers = 6, nstart = 25)
100 * model$betweenss / model$totss
```
### 58.63% stay in their cluster.
```{r}
cl <- kmeans(Cereals[4:12], centers = 6, nstart = 25)
Cereals <- data.frame(Cereals, cl$cluster)
cl$centers
```

### The data should be standardized since when it comes to what we eat, we should value what we put into our body. Cluster 1 is probably the most healthy, since it is high in protien, fiber, potassium and higher in vitamins. And less carboydrates and low calories.



